Topological Analysis of Bitcoin's Lightning Network

### 2019-01-07 article/main.tex
Added gitignore

\begin{wrapfigure}{r}{0.7\textwidth}
	\begin{center}
		\includegraphics[width=0.9\textwidth]{LNtopology.png}
	\end{center}
	\caption{LN's topology. Nodes with higher degree are highlighted with lighter colors}
	\vspace{-10pt}
\end{wrapfigure}

@@

\textbf{Our contributions.} We empirically measure and describe LN's topology and show that it is utterly centralized and fragile against both random failures and targeted attacks. These findings suggest that LN, unlike Bitcoin, is far from being reliable, censorship-resistant, decentralized and private.
\section{Lightning Network's Topology}
\begin{wrapfigure}[18]{r}{5.5cm}
	\begin{tabular}{ | l | c | }
		\hline
		Number of nodes & $2344$  \\ \hline
		Number of payment channels & $16617$  \\ \hline
		Connected components & $2$  \\ \hline
		Density & $0.00605$ \\ \hline
		Total BTC held in LN & $543.61855$\bitcoinA\\ \hline
		s-metric& $0.6878$ \\ \hline
		Maximal independent set & $1564$ \\ \hline
		Bridges & $530$ \\ \hline
		Diameter & $6$ \\ \hline
		Radius & $3$ \\ \hline
		Transitivity& $0.1046$\\ \hline
		Average clustering coefficient&$0.304$ \\ \hline
		Degree assortativity& $-0.2690$ \\ \hline
	\end{tabular}
	\caption{LN at a glance: basic properties of the LN graph.}\label{fig:properties}
\end{wrapfigure}

@@

LN gradually increased adoption and attraction throughout 2018, which resulted in 3 independent client implementations and \num[group-separator={,}]{2344} nodes joining LN as of 2019, January 3rd. The density of a graph is defined as $D=\frac{2\mid E\mid}{\mid V\mid \mid V-1\mid}$  which is the ratio of present and potential edges. As it is shown in Figure \ref{fig:properties}. LN is quite a parse graph. This is further justified by the fact that LN has \num[group-separator={,}]{530} bridges, edges which deletion increases the number of connected components. Although LN is consisted of $2$ components, the second component has only $3$ nodes. The low transitivity, fraction of present and possible triangles in the graph, highlights the sparseness of LN as well.

@@

\section{Robustness of LN}
\subsection{Random Failures}
\subsection{Targeted attacks}
\begin{figure}[h]
	\centering
	\begin{minipage}{.5\textwidth}
		\centering
		\includegraphics[width=\linewidth]{vertexConnectivity.png}
		\captionof{figure}{LN's vertex connectivity}
		\label{fig:test1}
	\end{minipage}%
	\begin{minipage}{.5\textwidth}
		\centering
		\includegraphics[width=\linewidth]{edgeConnectivity.png}
		\captionof{figure}{LN's edge connectivity}
		\label{fig:test2}
	\end{minipage}
\end{figure}

\subsection{Fixing LN's resilience against attacks}
percolation threshold
\section{Privacy}
topological anomalies have privacy implications, low usage of tor, even tor can not help
\section{Conclusion}
\section{Acknowledgements}

>>>>

\begin{wrapfigure}{r}{0.6\textwidth}
	\begin{center}
		\includegraphics[width=0.9\textwidth]{LNtopology.png}
	\end{center}
	\caption{LN's topology. Nodes with higher degree are highlighted with lighter colors}
	\vspace{-10pt}
\end{wrapfigure}

@@

\textbf{Our contributions.} We empirically measure and describe LN's topology and show that it is utterly centralized and fragile against both random failures and targeted attacks. These findings suggest that LN, unlike Bitcoin, is far from being reliable, censorship-resistant, decentralized and private.
\section{Lightning Network's Topology}
\begin{wrapfigure}[20]{r}{5.5cm}
	\begin{tabular}{ | l | c | }
		\hline
		Number of nodes & $2344$  \\ \hline
		Number of payment channels & $16617$  \\ \hline
		Average degree & $7.0891$ \\ \hline
		Connected components & $2$  \\ \hline
		Density & $0.00605$ \\ \hline
		Total BTC held in LN & $543.61855$\bitcoinA\\ \hline
		s-metric& $0.6878$ \\ \hline
		Maximal independent set & $1564$ \\ \hline
		Bridges & $530$ \\ \hline
		Diameter & $6$ \\ \hline
		Radius & $3$ \\ \hline
		Mean shortest path &  $2.80623$ \\ \hline
		Transitivity& $0.1046$\\ \hline
		Average clustering coefficient&$0.304$ \\ \hline
		Degree assortativity& $-0.2690$ \\ \hline
	\end{tabular}
	\caption{LN at a glance: basic properties of the LN graph.}\label{fig:properties}
\end{wrapfigure}

@@

LN gradually increased adoption and attraction throughout 2018, which resulted in 3 independent client implementations (c-lightning, eclair and lnd) and \num[group-separator={,}]{2344} nodes joining LN as of 2019, January 3rd. The density of a graph is defined as $D=\frac{2\mid E\mid}{\mid V\mid \mid V-1\mid}$  which is the ratio of present and potential edges. As it is shown in Figure \ref{fig:properties}. LN is quite a parse graph. This is further justified by the fact that LN has \num[group-separator={,}]{530} bridges, edges which deletion increases the number of connected components. Although LN is consisted of $2$ components, the second component has only $3$ nodes. The low transitivity, fraction of present and possible triangles in the graph, highlights the sparseness of LN as well.

@@

Average shortest path length is $2.80623$, which signals that payments can easily be routed with a few hops throughout the whole network. Although this is far from being a straightforward task, since one also needs to take into consideration the capacity of individual payment channels along a candidate path.

\section{Robustness of LN}
It is a major question in network science how robust a given network is. LN, just like Bitcoin, is a permissionless network, where nodes can join and leave arbitrarily at any point in time. Nodes can also create new payment channels or close them any time. Furthermore as new payments are made, capacities of payment channels are changing steadily. Despite the dynamic nature of LN, its topology's characteristics remain constant after all.
In this section we investigate how resilient is LN, whether it can effectively withhold random node failures or deliberate attacks.
\subsection{Random Failures}
\begin{wrapfigure}[15]{r}{5.5cm}
	\begin{tabular}{ | l | c | }
		\hline
		Network & $f_c$  \\ \hline
		Internet & $0.92$  \\ \hline
		WWW & $0.88$ \\ \hline
		US Power Grid & $0.61$  \\ \hline
		Mobil Phone Call & $0.78$ \\ \hline
		E-mail & $0.92$ \\ \hline
		Science collaboration& $0.92$ \\ \hline
		E. Coli Metabolism & $0.96$ \\ \hline
		Yeast Protein Interactions & $0.88$ \\ \hline
		LN & $0.00535$ \\ \hline
	\end{tabular}
	\caption{Random failures in networks. Values of critical thresholds for other real networks are taken from \cite{barabasi2016network}.}\label{fig:randfailures}
\end{wrapfigure}

Random failures are a realistic attack vector for LN. If nodes happen to be off-line due to bad connections or other reasons, they can not participate in routing payments anymore. Such a failure can be modeled as if a node and its edges are removed from the graph. We continually remove nodes from the graph, until the networks is broken into several isolated components. The fraction of nodes need to be removed from a network to break it into multiple connected components is called critical threshold and denoted as $f_c$. As Figure~\ref{fig:randfailures} displays LN is not capable of withstanding even random failures. This incapability is even more striking when compared to other real networks.

\subsection{Targeted attacks}
Targeted attacks on LN nodes are also a major concern as the short history of LN has already shown this. On 2018 March 21st \footnote{https://www.trustnodes.com/2018/03/21/lightning-network-ddos-sends-20-nodes}, $20\%$ of nodes were down due to a Distributed Denial of Service (DDoS) attack against LN nodes. Denial of Service (DoS) attacks are also quite probable by flooding HTLCs. These attack vectors are extremely harmful, especially if they are coordinated well. One might expect that not only state-sponsored attackers will have the resources to attack a small network like LN.   
\begin{figure}[h]
	\centering
	\begin{minipage}{.5\textwidth}
		\centering
		\includegraphics[width=\linewidth]{vertexConnectivity.png}
		\captionof{figure}{LN's vertex connectivity}
		\label{fig:test1}
	\end{minipage}%
	\begin{minipage}{.5\textwidth}
		\centering
		\includegraphics[width=\linewidth]{edgeConnectivity.png}
		\captionof{figure}{LN's edge connectivity}
		\label{fig:test2}
	\end{minipage}
\end{figure}

\subsection{Fixing LN's resilience against attacks}
percolation threshold
\section{Privacy}
topological anomalies have privacy implications, low usage of tor, even tor can not help
\section{Conclusion}
false sense of security and robustness
\section{Acknowledgements}
